---
title: "CIUS18"
output: html_document
date: "2023-09-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# THE FILE 
This file is the analysis done on the 2018 version of CIUS. 
Publicly available: https://abacus.library.ubc.ca/dataset.xhtml?persistentId=hdl:11272.1/AB2/KWDCXH

According to the accompanying documentation, the following are true: 

### SURVEY DESIGN
CIUS2018 was administered in 2018 from November 15th, 2018 to March 21, 2019. 

- Each of the 10 provinces were divided into strata. 
- Each record (telephone number) was assigned to a stratum within its province. 
- A simple random sample without replacement of records was next selected in each stratum. 

What does this mean? 
- Each telephone number (household) was assigned to a stratum within its province. 
- Each province is also a stratum. 
- Then a simple random sample without replacement of records was selected from each stratum within each province. 

**The documentation does not make it clear whether it is a two phased sampling design or a two stage sampling design --- to avoid making a mistake, both designs should be tested and the design that produces the correct results should be picked. However, the 2 phase sampling design cannot be implemented with the current information: **

So, if it is a 2 phase sampling design: 
Phase 1: Each province is broken into strata, *but no information on how this is done is shared, therefore whatever I come up with will be guess-work* -- phone numbers are assigned to each stratum within the provinces 
Phase 2: A simple random sample of the records are selected from each stratum within each province, which are strata themselves. 

Therefore, the 2 stage sampling design is defined here: 

- Each record in the sample is assigned to a stratum within its province. (Stage 1)
- In each stratum, a simple random sample without replacement is selected. (Stage 2)

Stage 1: Stratified Sampling (Strata: province)
Stage 2: Simple Random Sample without replacement : subset is households 


---
---
---

### Required Packages: 
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(survey)
library(haven)
library(rempsyc)
library(broom)
library(report)
library(effectsize)
library(svyVGAM)
library(aod)
library(readr)
library(tidymodels)
library(stargazer)
```

### DATA ANALYSIS 
```{r}
cius18 <- read_dta("cius_2018_en.dta")
```

#### Some information about the dataset: 
```{r}
print("Class:")
print(class(cius18))

print("Dimensions:")
print(dim(cius18))

```
There are 13,810 rows of data and 1,426 columns (1000 of which are bootstrap weights, leaving 426 questions on the survey). 

#### Making sure types are correct: 
The variables I'll need for design of sampling are province and a few new variables I'll declare myself. However, I'll first make sure that province is viewed as a factor. 

```{r}
cius18$province <- as.factor(cius18$province)
```

#### STAGE 1 - Unstratified variable: 
Just added a variable that is the same across all - because first stage isn't stratified. 
```{r}
cius18 <- cius18 %>% 
    mutate(unstra_new_var = 1)

head(cius18$unstra_new_var)
```
Generating some phone numbers: 
```{r}
#generate 33,248 phone numbers: 10 digits 
field_sample_phone_numbers <- seq(from = 1000000000, to = 1000033247, by = 1)

#randomly sample 13,810 of these 
phone_numbers <- sample(field_sample_phone_numbers, 13810, replace = FALSE)

```

Then add these to the dataset: 
```{r}
#add the phone_numbers to cius 
cius18 <- cius18 %>%
    mutate(phone = phone_numbers)

#make sure it is a factor 
cius18$phone <- as.factor(cius18$phone)
```

### SAMPLING DESIGN: 
```{r}
sample_design <- svydesign(
    id = ~phone + 1,
    data = cius18,
    strata = ~province + factor(unstra_new_var), 
    weights = ~NULL + wtpm
)
```

```{r}
sample_design 
```
Checking if this worked correctly. 

Employment: 
```{r}
svytotal(
    ~factor(emp),
    sample_design
)
```
Which is exactly the same numbers as the documentation. 







