---
title: "Dissertation"
output:
  html_document: default
date: "2023-08-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Required Packages: 
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(survey)
library(haven)
library(rempsyc)
library(broom)
library(report)
library(effectsize)
library(svyVGAM)
library(aod)
library(readr)
library(tidymodels)
library(stargazer)
```

### Dataset: 
```{r}
cius20 <- read_dta('cius2020_2022nov18_en.dta')
```


#### Some information about the dataset: 
```{r}
print("Class:")
print(class(cius20))

print("Dimensions:")
print(dim(cius20))

```
- There are 17,409 records
- There are 1,356 columns 


## SURVEY DESIGN

I'm assuming based on the documentation that the design is: 
- Each record in the sample is assigned to a stratum within its province. (Stage 1)
- Each stratum : a simple random sample without replacement is selected. (Stage 2)

Stage 1: Stratified Sampling (Strata: province)
Stage 2: Simple Random Sample without replacement : subset is households 

Before anything, I have to make sure province and G_HCOMP are both factors. 

```{r}

cius20$province <- as.factor(cius20$province)
cius20$g_hcomp <- as.factor(cius20$g_hcomp)
cius20$pumfid <- as.factor(cius20$pumfid)
```

Define a variable for the unstratified stage:
```{r}
cius20 <- cius20 %>%
    mutate(unstra = 1)

head(cius20$unstra)
```
Weights for the provinces being chosen based on the % of respondents. 
```{r}
cius20 <- cius20 %>%
    mutate(prov_wght = case_when(
        province == '10' ~ 1.4,
        province == '11' ~ 0.4,
        province == '12' ~ 2.6,
        province == '13' ~ 2.1,
        province == '24' ~ 22.6,
        province == '35' ~ 39.2,
        province == '46' ~ 3.5,
        province == '47' ~ 3.0,
        province == '48' ~ 11.4,
        province == '59' ~ 13.9
    ))
```

Forget about all of that; the real data should have: 

```{r}
#generate 44,800 phone numbers: 10 digits 
field_sample_phone_numbers <- seq(from = 1000000000, to = 1000044800, by = 1)

#randomly sample 17,409 of these 
phone_numbers <- sample(field_sample_phone_numbers, 17409, replace = FALSE)

```

```{r}
#add the phone_numbers to cius 
cius20 <- cius20 %>%
    mutate(phone = phone_numbers)

#make sure it is a factor 
cius20$phone <- as.factor(cius20$phone)
```

Now, the sample design is: 

```{r}
sampling_design <- svydesign(
    id = ~phone + 1,
    data = cius20,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

```{r}
sampling_design
```
```{r}
svytotal(
    ~factor(emp),
    sampling_design
)
```
Which is entirely correct! 

## Variable Segmentation 

It's important to separate the factors from the continuous variables. 

**CONTINUOUS**
```{r}
cius_continuous <- cius20 %>%
    select(ec_g010a, ec_g010b, ec_g010c, ec_g010d, ec_g010e, ec_g010f, ec_g010g, ec_g010h, ec_g010i, ec_g010j, ec_g010k, ec_g010l, ec_g010x, ec_g020a, ec_g050b, ec_g060a, sum_gtot)

```

**CATEGORICAL**

```{r}
cius_cateogrical <- cius20 %>%
    select(!c(ec_g010a, ec_g010b, ec_g010c, ec_g010d, ec_g010e, ec_g010f, ec_g010g, ec_g010h, ec_g010i, ec_g010j, ec_g010k, ec_g010l, ec_g010x, ec_g020a, ec_g050b, ec_g060a, sum_gtot))

```

```{r}
dim(cius_cateogrical)
```

Now, apply the factorization function to all the categorical variables: 

```{r}
#cius_cateogrical <- cius_cateogrical %>%
 #   mutate(across(1:1343, as.factor))
```

Do this to the cius20 data: 

```{r}
cius20 <- cius20 %>%
    mutate_at(vars(-c(ec_g010a, ec_g010b, ec_g010c, ec_g010d, ec_g010e, ec_g010f, ec_g010g, ec_g010h, ec_g010i, ec_g010j, ec_g010k, ec_g010l, ec_g010x, ec_g020a, ec_g050b, ec_g060a, sum_gtot, wtpg)), as.factor)
```

Testing this: 
```{r}
glimpse(cius20$int_use)
glimpse(cius20$gender)
glimpse(cius20$sum_gtot)
```
## Data Analysis

A look at our dependent variable: 
```{r}
glimpse(cius20$ui_050d)
```
6 : valid skip 
9 : not stated 

I will turn this into a binary variable: 
```{r}
library(caret)
```

```{r}
cius20_binary <- cius20 %>%
    filter(ui_050d == '1' | ui_050d == '2')

dim(cius20_binary)
```


```{r}
#replace all 6's and 9's with nothing

cius20_binary$ui_050d <- recode(
    cius20_binary$ui_050d,
    recodes = "2=0; 1=1; else=''"
)
```

check factor: 
```{r}
glimpse(cius20_binary$ui_050d)
```
But, when you select a '6': 
```{r}
cius20_binary %>%
    select(ui_050d) %>%
    filter(ui_050d == '6')
```

```{r}
cius20_binary %>%
    count(ui_050d)
```

Run a design on binary dataset: 

```{r}
cius20_binary <- cius20_binary %>% 
    mutate(wtpg = as.numeric(wtpg))
```

```{r}
binary_s_design <- svydesign(
    id = ~phone + 1,
    data = cius20_binary,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

Drop the bootstrap weights from the binary dataset: 
```{r}
#names of columns to drop: 
#glimpse(tail(cius20_binary))

# wrpg1 - wrpg1000
bin_data <- cius20_binary %>%
    select(!(wrpg1 : wrpg1000))

```

```{r}
s_b_design <- svydesign(
    id = ~phone + 1,
    data = bin_data,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

making sure it's binary (0's and 1's):
```{r}
#replace all 6's and 9's with nothing

bin_data$ui_050d <- recode(
    bin_data$ui_050d,
    recodes = "2=0; 1=1; else=''"
)
```


### Functions for Tabulation
```{r}
tabular_against_mbanking <- function(this_){
    tab <- svymean(
        ~interaction(
            ui_050d,
            this_,
            drop = TRUE
        ),
        s_b_design
    )
    
    return(tab)
}

prettify <- function(table_, this_, values){
    pretty <- ftable(
        table_,
        rownames = list(
            usage = c("Use M-banking", "Not use M-banking"),
            levels = values
        )
    )

    return(round(pretty * 100, 1))
}


```

### PRELIMINARY ANALYSIS 

All the next few thousand lines of code do the same thing based on the following function: They get a variable name, and build a cross-tabulation table. This function is only for "factor" or categorical variables.  

```{r}
build_cross_tab <- function(this_){
    #make the table 
    var_tab <- tabular_against_mbanking(this_)

    #get the factor levels 
    var_values <- levels(this_)
    
    #make the table pretty
    pretty_table_age <- prettify(var_tab, this_, var_values)

    return(pretty_table_age)
}

```


Starting from the first categorical variable: 

```{r}
build_cross_tab(bin_data$province)
```

```{r}
build_cross_tab(bin_data$luc_rst)
```

```{r}
build_cross_tab(bin_data$age_grp)
```

```{r}
build_cross_tab(bin_data$gender)
```
For example, this shows: On average --- 39.4% of men use mobile banking while 9.3% don't This is very close for women with 41.9% and 9.4% respectively. 

... do this for all variables. 

.
.
.

## CATEGORICAL VARIABLES - INDEPENDENT TEST
To test the independence use the $\chi^2$-Squared test. The $H_0$ is independence of the variables. (not related)

Again, going through the variables that are categorical; However, we must only use this on the actual dataset (no changes made to it : cius20, and sampling_design)

```{r}
glimpse(head(cius20$ui_050d))
```

```{r}
svychisq(
        ~ui_050d + province,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + luc_rst,
        sampling_design
    )
```

```{r}
svychisq(
        ~ui_050d + age_grp,
        sampling_design
    )
```

```{r}
svychisq(
        ~ui_050d + gender,
        sampling_design
    )
```
This means "gender" is unrelated. We can set it aside from the analysis, and we clearly saw this in the tabulation. 

```{r}
svychisq(
        ~ui_050d + home_use,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + g_abm,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + lan_g01,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + emp,
        sampling_design
    )
```
And so on for the rest of the categorical variables... 


### VISUALIZATIONS 
We can visualize the relationships: 

```{r}
#copy the dataset --- just for visualizations: 
library(stringr)

just_for_vis <- cius20 %>%
    mutate(ui_050d = str_replace(ui_050d, "1", "Use")) %>%
    mutate(ui_050d = str_replace(ui_050d, "2", "No_Use")) %>%
    mutate(ui_050d = str_replace(ui_050d, "6", "Skip")) %>%
    mutate(ui_050d = str_replace(ui_050d, "9", "NotStated"))
```

Visualizer for categorical variables: 
```{r}
svyboxplot(
    #m-banking usage vs variable 
    ui_050d ~ factor(emp), 
    col = "gray80",
    varwidth = TRUE, #change width based on numbers in the levels
    ylab = "M-banking Usage",
    xlab = "Employment",
    design = sampling_design
)
```

Most people are in the employed segment, and those are mostly around 1 (use bank). 


A closer look into the differences between the groups, similar to AB testing: 

```{r}
draw_for_ab_test <- function(this_, x_lab){
    palette <- c(Use = "#377EB8", No_Use = "#03f4fc", Skip = "black", NotStated = "gray80")

    plot_ <- ggplot(cius20, aes(factor(this_), fill = factor(ui_050d))) + geom_bar() + labs(x = x_lab, y = "Online Banking Usage") 
    
    scale_fill_manual("Usage", values = palette)
    
    return(plot_)
}
```

```{r}
draw_for_ab_test(cius20$emp, "Employment")
```












