---
title: "Dissertation"
output: html_document
date: "2023-08-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Required Packages: 
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(survey)
library(haven)
library(rempsyc)
library(broom)
library(report)
library(effectsize)
library(svyVGAM)
library(aod)
library(readr)
library(tidymodels)
library(stargazer)
```

### Dataset: 
```{r}
cius20 <- read_dta('cius2020_2022nov18_en.dta')
```


#### Some information about the dataset: 
```{r}
print("Class:")
print(class(cius20))

print("Dimensions:")
print(dim(cius20))

```
- There are 17,409 records
- There are 1,356 columns 


## SURVEY DESIGN

I'm assuming based on the documentation that the design is: 
- Each record in the sample is assigned to a stratum within its province. (Stage 1)
- Each stratum : a simple random sample without replacement is selected. (Stage 2)

Stage 1: Stratified Sampling (Strata: province)
Stage 2: Simple Random Sample without replacement : subset is households 

Before anything, I have to make sure province and G_HCOMP are both factors. 

```{r}

cius20$province <- as.factor(cius20$province)
cius20$g_hcomp <- as.factor(cius20$g_hcomp)
cius20$pumfid <- as.factor(cius20$pumfid)
```

Now, the subset for phase 2 is the houses that are 1,2,3. 
```{r}
#subset_phase2 <- sample(which(cius20$g_hcomp %in% c('1','2','3')), )

subset_phase2 <- cius20 %>% 
    filter(g_hcomp %in% c('1','2','3'))

head(subset_phase2$g_hcomp)
```




Define a variable for the unstratified stage:
```{r}
cius20 <- cius20 %>%
    mutate(unstra = 1)

head(cius20$unstra)
```
Weights for the provinces being chosen based on the % of respondents. 
```{r}
cius20 <- cius20 %>%
    mutate(prov_wght = case_when(
        province == '10' ~ 1.4,
        province == '11' ~ 0.4,
        province == '12' ~ 2.6,
        province == '13' ~ 2.1,
        province == '24' ~ 22.6,
        province == '35' ~ 39.2,
        province == '46' ~ 3.5,
        province == '47' ~ 3.0,
        province == '48' ~ 11.4,
        province == '59' ~ 13.9
    ))
```


```{r}
twostage_design <- svydesign(
    id = ~1 + 1,
    data = cius20,
    strata = ~province + unstra,
    weights = ~prov_wght + wtpg
)
```

Survey design: 
```{r}
twostage_design
```
A different version: 
```{r}
twostage_design_v01 <- svydesign(
    id = ~1 + g_hcomp,
    data = cius20,
    strata = ~province + unstra,
    weights = ~NULL + wtpg,
    nest = TRUE
)
```


```{r}
svytotal(
    ~gender,
    twostage_design
)
```

```{r}
svytotal(
    ~gender,
    twostage_design_v01
)
```
```{r}
twostage_design_v02 <- svydesign(
    id = ~1 + 1,
    data = cius20,
    strata = ~province + unstra,
    weights = ~NULL + wtpg
)
```


```{r}
svytotal(
    ~emp,
    twostage_design_v02
)
```
```{r}
twostage_design_v03 <- svydesign(
    id = ~1 + pumfid,
    data = cius20,
    strata = ~province + unstra,
    weights = ~NULL + wtpg
)
```

```{r}
svytotal(
    ~home_use,
    twostage_design_v03
)
```
Version 3 is the closest to the actual value:  33,505,139 with a total estimate of 31,635,259. 

I'll use this: twostage_design_v03 as the sampling design. 

```{r}
twostage_design_v05 <- svydesign(
    id = ~1 + factor(pumfid),
    data = cius20,
    strata = ~province + unstra,
    weights = ~NULL + wtpg
)
```

```{r}
svytotal(
    ~ed_g10,
    twostage_design_v05
)
```
Forget about all of that; the real data should have: 

```{r}
#generate 44,800 phone numbers: 10 digits 
field_sample_phone_numbers <- seq(from = 1000000000, to = 1000044800, by = 1)

#randomly sample 17,409 of these 
phone_numbers <- sample(field_sample_phone_numbers, 17409, replace = FALSE)

```

```{r}
#add the phone_numbers to cius 
cius20 <- cius20 %>%
    mutate(phone = phone_numbers)

#make sure it is a factor 
cius20$phone <- as.factor(cius20$phone)
```

Now, the sample design is: 

```{r}
sampling_design <- svydesign(
    id = ~phone + 1,
    data = cius20,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

```{r}
sampling_design
```
```{r}
svytotal(
    ~factor(emp),
    sampling_design
)
```
Which is entirely correct! 
















