---
title: "subset_selection_sm_user"
output: html_document
date: "2023-08-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(ggplot2)
library(survey)
library(haven)
library(rempsyc)
library(broom)
library(report)
library(effectsize)
library(readr)
library(tidymodels)
library(aod)
```
```{r}
cius <- read_dta('cius2020_2022nov18_en.dta')
```

```{r}
df <- data.frame(cius)
```

Select the ones that meet the following conditions: 
- smartphone use only 

step1. See all the device options in the dataset: 
```{r}
df %>% 
    select(matches("dv_010"))
```

Those are:
- smartphone
- laptop
- tablet 
- pc 
- media streaming device 
- smart TV
- internet-connected wearable smart device 
- connected vehicle 
- other devices 

Only selecting those that use smartphone but nothing else: 
```{r}
df %>% 
    filter(
        dv_010a == 1.0 & dv_010b != 1.0 & dv_010c != 1.0 & dv_010d != 1 & dv_010d != 1.0 & dv_010e != 1.0 
        & dv_010f != 1.0 & dv_010g != 1.0 & dv_010h != 1.0 & dv_010i != 1
        )
```
That is 1,015 rows of the dataset. 

```{r}
only_sm_users <- 1015
total_users <- 17409 

print('percentage of only smartphone users data available: ')
print((only_sm_users/total_users) * 100)
```
Only about 6%. If we consider the tablet + smartphone users...
```{r}
df %>% 
    filter(
        (dv_010a == 1.0 | dv_010c == 1.0) & (dv_010b != 1.0 & dv_010d != 1 & dv_010d != 1.0 & dv_010e != 1.0 
        & dv_010f != 1.0 & dv_010g != 1.0 & dv_010h != 1.0 & dv_010i != 1
        ))
```

```{r}

tab_sm_users <- 2029

print('percentage of tablet or smartphone users data available: ')
print((tab_sm_users/total_users) * 100)
```
That's basically only 12% of the data. Just over 2000 rows of data. 

Let's say I save this into a dataset called "tabSM" and proceed with the previous analysis on this dataset: 
```{r}
tabSM <- df %>% 
    filter(
        (dv_010a == 1.0 | dv_010c == 1.0) & (dv_010b != 1.0 & dv_010d != 1 & dv_010d != 1.0 & dv_010e != 1.0 
        & dv_010f != 1.0 & dv_010g != 1.0 & dv_010h != 1.0 & dv_010i != 1
        ))
```

```{r}
tabSM$province <- as.factor(tabSM$province)
tabSM$g_hcomp <- as.factor(tabSM$g_hcomp)
tabSM$pumfid <- as.factor(tabSM$pumfid)
tabSM$ui_050d <- as.factor(tabSM$ui_050d)
```

Define a variable for the unstratified stage:
```{r}
tabSM <- tabSM %>%
    mutate(unstra = 1)

head(tabSM$unstra)
```


```{r}
#generate 44,800 phone numbers: 10 digits 
field_sample_phone_numbers <- seq(from = 1000000000, to = 1000044800, by = 1)

#randomly sample 17,409 of these 
phone_numbers <- sample(field_sample_phone_numbers, 2029, replace = FALSE)

```

```{r}
#add the phone_numbers to cius 
tabSM <- tabSM %>%
    mutate(phone = phone_numbers)

#make sure it is a factor 
tabSM$phone <- as.factor(tabSM$phone)
```

Now, the sample design is: 

```{r}
sampling_design <- svydesign(
    id = ~phone + 1,
    data = tabSM,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

```{r}
sampling_design
```

## Variable Segmentation 

It's important to separate the factors from the continuous variables. 

**CONTINUOUS**
```{r}
cius_continuous <- tabSM %>%
    select(ec_g010a, ec_g010b, ec_g010c, ec_g010d, ec_g010e, ec_g010f, ec_g010g, ec_g010h, ec_g010i, ec_g010j, ec_g010k, ec_g010l, ec_g010x, ec_g020a, ec_g050b, ec_g060a, sum_gtot)

```

**CATEGORICAL**

```{r}
cius_cateogrical <- tabSM %>%
    select(!c(ec_g010a, ec_g010b, ec_g010c, ec_g010d, ec_g010e, ec_g010f, ec_g010g, ec_g010h, ec_g010i, ec_g010j, ec_g010k, ec_g010l, ec_g010x, ec_g020a, ec_g050b, ec_g060a, sum_gtot))

```

```{r}
dim(cius_cateogrical)
```

```{r}
library(caret)

```

```{r}
tab_binary <- tabSM %>%
    filter(ui_050d == '1' | ui_050d == '2')

dim(tab_binary)
```


```{r}
#replace all 6's and 9's with nothing
tab_binary$ui_050d <- recode(
    tab_binary$ui_050d,
    recodes = "2=0; 1=1;else=''"
)
```

check factor: 
```{r}
glimpse(tab_binary$ui_050d)
```
But, when you select a '6': 
```{r}
tab_binary %>%
    select(ui_050d) %>%
    filter(ui_050d == '6')
```

```{r}
tab_binary %>%
    count(ui_050d)
```

Run a design on binary dataset: 

```{r}
tab_binary <- tab_binary %>% 
    mutate(wtpg = as.numeric(wtpg))
```

```{r}
binary_s_design <- svydesign(
    id = ~phone + 1,
    data = tab_binary,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

Drop the bootstrap weights from the binary dataset: 
```{r}
#names of columns to drop: 
#glimpse(tail(cius20_binary))

# wrpg1 - wrpg1000
bin_data <- tab_binary %>%
    select(!(wrpg1 : wrpg1000))

```

```{r}
s_b_design <- svydesign(
    id = ~phone + 1,
    data = bin_data,
    strata = ~province + factor(unstra),
    weights = ~NULL + wtpg
)
```

making sure it's binary (0's and 1's):
```{r}
#replace all 6's and 9's with nothing

bin_data$ui_050d <- recode(
    bin_data$ui_050d,
    recodes = "2=0; 1=1; else=''"
)
```


### Functions for Tabulation
```{r}
tabular_against_mbanking <- function(this_){
    tab <- svymean(
        ~interaction(
            ui_050d,
            this_,
            drop = TRUE
        ),
        s_b_design
    )
    
    return(tab)
}

prettify <- function(table_, this_, values){
    pretty <- ftable(
        table_,
        rownames = list(
            usage = c("Use M-banking", "Not use M-banking"),
            levels = values
        )
    )

    return(round(pretty * 100, 1))
}


```

### PRELIMINARY ANALYSIS 

All the next few thousand lines of code do the same thing based on the following function: They get a variable name, and build a cross-tabulation table. This function is only for "factor" or categorical variables.  

```{r}
build_cross_tab <- function(this_){
    #make the table 
    var_tab <- tabular_against_mbanking(this_)

    #get the factor levels 
    var_values <- levels(this_)
    
    #make the table pretty
    pretty_table_age <- prettify(var_tab, this_, var_values)

    return(pretty_table_age)
}

```


Starting from the first categorical variable: 

```{r}
build_cross_tab(bin_data$province)
```

```{r}
bin_data$age_grp <- as.factor(bin_data$age_grp)
build_cross_tab(bin_data$age_grp)
```
```{r}
bin_data$emp <- as.factor(bin_data$emp)
build_cross_tab(bin_data$emp)
```


... do this for all variables. 

.
.
.

## CATEGORICAL VARIABLES - INDEPENDENT TEST
To test the independence use the $\chi^2$-Squared test. The $H_0$ is independence of the variables. (not related)

Again, going through the variables that are categorical; However, we must only use this on the actual dataset (no changes made to it : cius20, and sampling_design)

```{r}
glimpse(head(tabSM$ui_050d))
```

```{r}
svychisq(
        ~ui_050d + province,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + age_grp,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + emp,
        sampling_design
    )
```
```{r}
svychisq(
        ~ui_050d + gender,
        sampling_design
    )
```

Alright, it's working as I had expected! 







