---
title: "subset_selection_sm_user"
output: html_document
date: "2023-08-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(ggplot2)
library(survey)
library(haven)
library(rempsyc)
library(broom)
library(report)
library(effectsize)
library(readr)
library(tidymodels)
library(aod)
```
```{r}
cius <- read_dta('cius2020_2022nov18_en.dta')
```

```{r}
df <- data.frame(cius)
```

Select the ones that meet the following conditions: 
- smartphone use only 

step1. See all the device options in the dataset: 
```{r}
df %>% 
    select(matches("dv_010"))
```

Those are:
- smartphone
- laptop
- tablet 
- pc 
- media streaming device 
- smart TV
- internet-connected wearable smart device 
- connected vehicle 
- other devices 

Only selecting those that use smartphone but nothing else: 
```{r}
df %>% 
    filter(
        dv_010a == 1.0 & dv_010b != 1.0 & dv_010c != 1.0 & dv_010d != 1 & dv_010d != 1.0 & dv_010e != 1.0 
        & dv_010f != 1.0 & dv_010g != 1.0 & dv_010h != 1.0 & dv_010i != 1
        )
```
That is 1,015 rows of the dataset. 

```{r}
only_sm_users <- 1015
total_users <- 17409 

print('percentage of only smartphone users data available: ')
print((only_sm_users/total_users) * 100)
```
Only about 6%. If we consider the tablet + smartphone users...
```{r}
df %>% 
    filter(
        (dv_010a == 1.0 | dv_010c == 1.0) & (dv_010b != 1.0 & dv_010d != 1 & dv_010d != 1.0 & dv_010e != 1.0 
        & dv_010f != 1.0 & dv_010g != 1.0 & dv_010h != 1.0 & dv_010i != 1
        ))
```

```{r}

tab_sm_users <- 2029

print('percentage of tablet or smartphone users data available: ')
print((tab_sm_users/total_users) * 100)
```
That's basically only 12% of the data. Just over 2000 rows of data. 














